---
title: "HW3"
author: "Stephen Powers"
date: "10/12/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(viridis)
```


```{r data, include=FALSE}
library(p8105.datasets)
data("instacart")
data("brfss_smart2010")
```

## Problem 1

#### *Cleaning Instacart Dataset*

```{r echo=FALSE}
instacart %>% 
  janitor::clean_names() %>% 
  head() %>% 
  knitr::kable(
    caption = "**Table 1**: Instacart Dataset"
  )
```

The `instacart` dataset contains `r nrow(instacart)` observations and `r ncol(instacart)` variables. The variables in the dataset includes the following: `r colnames(instacart)`

* There are `r length(unique(pull(instacart, aisle)))` total aisles in the dataset. 

```{r echo=FALSE}
instacart %>% 
  select(product_id, product_name, aisle) %>% 
  count(product_id, product_name, aisle) %>% 
  arrange(desc(n)) %>% 
  head(15) %>% 
  knitr::kable(
    caption = "**Table 2**: Most ordered items"
  )
```

* From the table created above, we see that the most ordered items are from the "fresh fruits" and "packaged vegetables fruits" aisles. 


```{r plot1, echo=FALSE}
instacart %>% 
  group_by(aisle) %>% 
  count() %>% 
  filter(n > 10000) %>% 
  ggplot(aes(x = reorder(aisle, n), y = n)) +
  geom_bar(stat = "identity") +
  theme_classic() +
  ggtitle("Number of Items Ordered in Each Aisle") +
  xlab("Aisle") +
  ylab("Number of items ordered") +
  theme(axis.text.x = element_text(angle=45, hjust=1))
```

#### *Creating a table showing the three most popular items in each of the aisles “baking ingredients”, “dog food care”, and “packaged vegetables fruits”.*

```{r echo=FALSE}
instacart %>% 
  filter(aisle == c("baking ingredients","dog food care","packaged vegetables fruits")) %>%
  group_by(aisle, product_name) %>% 
  summarize(
    number_orders = n()) %>% 
  arrange(aisle, desc(number_orders)) %>% 
  mutate(rank = rank(desc(number_orders))) %>% 
  filter(rank<4) %>% 
  pivot_wider(
    id_cols = rank,
    names_from = aisle,
    values_from = c(product_name, number_orders)) %>% 
  knitr::kable(
    caption = "**Table 3**: Three most popular items in each of the aisles baking ingredients, dog food care, and packaged vegetables fruits"
  )
```

#### *Creating a table showing the mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered on each day of the week*

```{r echo=FALSE}
instacart %>% 
  select(product_name, order_hour_of_day, order_dow) %>% 
  filter(product_name %in% c("Pink Lady Apples", "Coffee Ice Cream")) %>% 
  mutate(order_dow = as.factor(order_dow)) %>% 
  mutate(
        day = recode(order_dow,
            "0" = "Sunday",
            "1" = "Monday",
            "2" = "Tuesday",
            "3" = "Wednesday",
            "4" = "Thursday",
            "5" = "Friday",
            "6" = "Saturday")
        ) %>% 
  group_by(product_name, day) %>% 
  arrange(product_name, day) %>% 
  summarize(
    mean_hour = mean(order_hour_of_day)) %>% 
  pivot_wider(
    id_cols = "product_name",
    names_from = "day",
    values_from = "mean_hour",
    ) %>% 
  knitr::kable(
    caption = "**Table 4**: Mean hour of the day at which Pink Lady Apples and Coffee Ice Cream are ordered")
```


## Problem 2

#### *Renaming and cleaning data `brfss_smart2010`*

```{r echo=FALSE}
brfss =
  brfss_smart2010 %>% 
    janitor::clean_names() %>% 
    rename(
      state = locationabbr,
      descending_location = locationdesc,
    )
```

#### *Formatting a new dataset to focus on the “Overall Health” topic*

```{r echo=FALSE}
brfss_new = 
  brfss %>% 
    filter(
      topic == "Overall Health",
      response %in% c("Excellent", "Very good", "Good", "Fair", "Poor")) %>%
    mutate(response = ordered(as.factor(response),
                              levels = c(
                                "Poor", 
                                "Fair", 
                                "Good", 
                                "Very good", 
                                "Excellent")))
```


#### *Creating a table for states that were observed at 7 or more location in 2002*

```{r echo=FALSE}
brfss_new %>% 
  select(state, descending_location, year) %>% 
  filter(year == 2002) %>% 
  unique() %>%
  group_by(state) %>%
  summarize(
    number_locations = n()) %>% 
    filter(number_locations >= 7) %>% 
  knitr::kable(
  caption = "**Table 5**: States that were observed at 7 or more locations (year =2002)"
  )
```

#### *Creating a table for states that were observed at 7 or more location in 2010*

```{r echo=FALSE}
brfss_new %>% 
  select(state, descending_location, year) %>% 
  filter(year == 2010) %>% 
  unique() %>%
  group_by(state) %>%
  summarize(
    number_locations = n()) %>% 
    filter(number_locations >= 7) %>% 
  knitr::kable(
  caption = "**Table 6**: States that were observed at 7 or more locations (year = 2010)"
  )
```

#### *Creating Spaghetti Plot*

```{r warning=FALSE, echo=FALSE}
brfss_new %>% 
  filter(response == "Excellent") %>% 
  select(year, state, descending_location, data_value) %>%
  group_by(year, state) %>%
  summarize(
    mean_data_value = mean(data_value)) %>% 
  ggplot(aes(x = year, y = mean_data_value, group = state, color = state)) +
  geom_line() +
  ggtitle("Spaghetti Plot") +
  theme_classic() +
  theme(
    plot.title = element_text(hjust = 0.5)) +
  xlab("Year") +
  ylab("Mean Percent of People Indicating 'Excellent' Overall Health")
```

#### *Creating two-panel plot*

```{r}
brfss_new %>% 
    mutate(descending_location = str_to_title(descending_location)) %>% 
    filter(
        year %in% c(2006, 2010),
        state == "NY") %>% 
        group_by(year, descending_location) %>%
    ggplot(aes(x = response, y = data_value, fill = descending_location)) + 
    geom_col(position = "dodge") + 
    facet_grid(. ~ year) +
    viridis::scale_fill_viridis(
        option = "magma",
        name = "County",
        discrete = TRUE) +
    labs(
        title = "Distribution of Response Values by Year and NY County",
        x = "Response",
        y = "Mean Response Value") +
    theme_classic() +
    theme(axis.text.x = element_text(angle=45, hjust=1))
```


## Problem 3

#### *Load in Accel Data*
```{r include=FALSE}
accel_data = read_csv("./Data/accel_data.csv")
```

#### *Cleaning Accel Data*

```{r echo=FALSE}
accel = 
  accel_data %>% 
  janitor::clean_names() %>% 
  pivot_longer(
    activity_1:activity_1440,
    names_to = "minute",
    names_prefix = "activity_",
    values_to = "activity") %>% 
  mutate(day_type = if_else(day %in% c("Saturday", "Sunday"),"weekend", "weekday"),
    day_type = as.factor(day_type),
    minute = as.numeric(minute),
    activity = as.numeric(activity), 
    minute = as.numeric(minute),
    day = as.factor(day), 
    week = as.factor(week),
    day_id = as.numeric(day_id)) %>% 
  view()
```

This dataset, Accel, contains `r nrow(accel)` observations. There are `r ncol(accel)` variables in this dataset. These variables include the following: `r colnames(accel)`.

#### *Creating Table for Total Activity*

```{r echo=FALSE}
accel %>% 
  group_by(week, day) %>% 
  summarise(
    total_activity = sum(activity)) %>% 
  knitr::kable(col.names = c("Week", "Day", "Total Activity"),
  caption = "**Table 7**: Daily Activity")
```
