---
title: "HW3"
author: "Stephen Powers"
date: "10/12/2019"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```



```{r data, include=FALSE}
library(p8105.datasets)
data("instacart")
data("brfss_smart2010")
```

## Problem 1

###*Cleaning Instacart Dataset*

```{r echo=FALSE}
instacart %>% 
  janitor::clean_names() %>% 
  head() %>% 
  knitr::kable()
```

The `instacart` dataset contains `r nrow(instacart)` observations and `r ncol(instacart)` variables. The variables in the dataset includes the following: `r colnames(instacart)`

* There are `r length(unique(pull(instacart, aisle)))` total aisles in the dataset. 

```{r echo=FALSE}
instacart %>% 
  select(product_id, product_name, aisle) %>% 
  count(product_id, product_name, aisle) %>% 
  arrange(desc(n)) %>% 
  head(15) %>% 
  knitr::kable()
```

* From the table created above, we see that the most ordered items are from the "fresh fruits" and "packaged vegetables fruits" aisles. 

## Problem 2


```{r }

```


## Problem 3


```{r}

```


